\documentclass[letter]{article}
\usepackage{microtype}
\usepackage{fullpage}
\usepackage{url}

\title{\\
  Computer Science Department\\
  Ball State University\\
  Technical Report 2017--01}

\author{
  Chas Busenburg
  \and
  Paul Gestwicki
  \and
  Ying Liu
  \and
  Jacob Rendall}

\begin{document}

\begin{centering}
{\Large A requirements and design analysis for an interactive online donation interface}\\
\vspace{0.5cm}
Chas Busenburg, Paul Gestwicki\footnote{Corresponding author}, Ying Liu, and Jacob Rendall\\
Computer Science Department\\
\texttt{cwbusenburg@bsu.edu}, 
\texttt{pvgestwicki@bsu.edu},
\texttt{yliu12@bsu.edu},
\texttt{jbrendall@bsu.edu}\\
\vspace{0.5cm}
\today\\
\vspace{0.5cm}
Computer Science Department\\
Ball State University\\
Technical Report 2017--01\\
\end{centering}

\section*{Introduction}

ecoREHAB is a nonprofit organization in Muncie, Indiana, that specializes
in environmentally-friendly, economically-sound rehabilitation of houses.
The organization started as an immersive learning project at Ball
State University in 2009, as a collaboration between the 
City of Muncie Department of Community Development and the 
Ball State College of Architecture and Planning.
ecoREHAB was successful enough to become an independent non-profit, 
although it maintains partnerships with the university.
Their mission statement is given below.

\begin{quote}
  Our Mission is to provide leadership in ecologically sound and
  sustainable rehabilitation of existing housing and
  neighborhoods. ecoREHAB of Muncie, Inc. will engage in activities
  that include: 1)~acquisition and ecologically sustainable
  rehabilitation of affordable housing; 2)~provide resources to aid
  homeowners and in rehabilitation of existing housing following
  sustainable design, material and system strategies; and 3)~other
  activities relative to housing that help the community to achieve
  the triple-bottom-line of economic prosperity, environmental
  protection, and social equity.
\end{quote}

In Spring 2017, Kate Elliott led an undergraduate team of journalism,
marketing, and public relations students in a new immersive learning
partnership with ecoREHAB, with the goal of revising the organization's
branding and Web presence.
ecoREHAB has been primariliy grant-funded, and one of the 
goals for the revised Web site was to accept donations from
the community, including local residents and university alumni.


\section*{Design}

\section*{Conclusions and Future Work}

\section*{Appendix}

\end{document}
